`flippant` -- An `R` package for the automated analysis of dithionite scramblase

### 2015-10-01 inst/manuscript/manuscript.rmd
Clarify intended usage for the generic data format (in response to remark by Mike Goren);
Fix a superfluous comma;

Spectral input data is read by `flippant` using the file paths provided in the
spreadsheet. Raw spectra produced by QuantaMaster fluorometer instruments 
(Photon Technology International, Inc., Edison, New Jersey) running software 
versions FelixGX v4.1 and Felix32 v1.20, respectively, as well as a simple 
generic tab-delimited spectrum representing file format with time (in seconds) 
and fluorescence intensity representing columns are currently supported. 
File type determination is handled algorithmically.

@@

Mean values of fit constant $\alpha$ correspond with 
`r ppr_results_alpha_average_print` for `r ppr_results_alpha_average_names`, 
respectively, very well to the prior manual analysis by 
@ploier_perturbed_submitted, where $\alpha \approx 0.13$ was reported for mutant 
and $\alpha \approx 0.26$ for wild type rhodopsin. Based on the manual analysis 
of the data we conclude in @ploier_perturbed_submitted that the mutant 
rhodopsins investigated are reconstituted into proteoliposomes in monomeric 
form, contrary to the wild type, which is reconstituting as a homodimer. 
`flippant` analysis of the data, shows identical trends and close matches of the
results, supporting identical conclusions.

>>>>

Spectral input data is read by `flippant` using the file paths provided in the
spreadsheet. Raw spectra produced by QuantaMaster fluorometer instruments 
(Photon Technology International, Inc., Edison, New Jersey) running software 
versions FelixGX v4.1 and Felix32 v1.20, respectively, as well as a simple 
generic tab-delimited spectrum representing file format with time (in seconds) 
and fluorescence intensity representing columns are currently supported. The 
latter is trivially assembled from any fluorescence data using a spreadsheet 
program. File type determination is handled algorithmically.

@@

Mean values of fit constant $\alpha$ correspond with 
`r ppr_results_alpha_average_print` for `r ppr_results_alpha_average_names`, 
respectively, very well to the prior manual analysis by 
@ploier_perturbed_submitted, where $\alpha \approx 0.13$ was reported for mutant 
and $\alpha \approx 0.26$ for wild type rhodopsin. Based on the manual analysis 
of the data we conclude in @ploier_perturbed_submitted that the mutant 
rhodopsins investigated are reconstituted into proteoliposomes in monomeric 
form, contrary to the wild type, which is reconstituting as a homodimer. 
`flippant` analysis of the data shows identical trends and close matches of the
results, supporting identical conclusions.
